---
title: "analyses"
author: "Maxwel Coura Oliveira"
date: "10/12/2021"
output: html_document
---

>  The biggest question to answer would be whether soybean (across varieties) are more sensitive to metribuzin or sulfentrazone; farmers are typically concerned about metribuzin but in recent conversations with several weed scientists it seems like that current soybean varieties handle metribuzin well; the problem is usually sulfentrazone/flumi (splashing during emergence); that's what Nikola's paper indicated

```{r}
library(tidyverse)
library(ggthemes)
library(ggtext)
library(rstanarm)
library(brms)
library(scales)
library(bayestestR)
library(BayesFactor)
library(emmeans)
library(glmmTMB)
library(lmerTest)
```


```{r}
read_csv("data/soytolerance.csv") |> 
  janitor::clean_names() |> 
  mutate(rating = parse_double(rating)) |> 
  mutate(rating = if_else(rating > 10, 
                          NA_real_, rating)) |> 
  mutate(rating = rating / 10) |> 
  mutate(rating = case_when(
    rating == 0.0 ~ 0.1,
    rating == 1.0 ~ 0.99,
    TRUE ~ rating
  )) |> 
  mutate_if(is_character, as_factor) |> 
  mutate(herbicide = fct_recode(herbicide,
                                "Untreated" = "ctrl",
                                "Metribuzin" = "metr",
                                "Sulfentrazone" = "sulf")) |> 
  mutate(rate_id = case_when(
    rating >= 0.7 ~ "Health",
    rating < 4 ~ "Injury",
    TRUE ~ "Median"
  )) -> data
```

```{r}
data |> 
  count(rate_id, herbicide, herb_trait) |> 
  group_by(herb_trait, herbicide) |> 
  mutate(sum = sum(n)) |> 
  mutate(perc = round(n / sum, 2)) |> 
  ggplot(aes(x = herb_trait, y = perc, fill = rate_id)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(~herbicide) +
  coord_flip()
```




```{r}
data1 <- data |> 
  nest(-herb_trait)
```


```{r}
mod_func <- function(dt){
glmmTMB(rating ~ herbicide + (1|run/variety), 
        family = beta_family(),
        data = dt
        )
}
```

```{r}
data1 |> 
  mutate(model = map(data, mod_func),
         anova = map(model, glmmTMB:::Anova.glmmTMB)) -> data2
```



```{r}
data2$model[[1]]
```


```{r}
emmip(data2$model[[1]], ~ herbicide, type = "response") +
  coord_flip()
```

```{r}
emmeans(model, ~ herbicide, type = "response") -> emm1
```

```{r}
plot(emm1, ~ herbicide, 
     comparisons=TRUE, 
     type="response", 
     alpha=0.05, 
     adjust="none") +
  scale_x_continuous(limits = c(0, 1), labels = scales::number_format(scale = 10))
```

```{r}
library(multcomp)
cld <- cld(emm1, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld
```



```{r}
emm1 |> 
  as_tibble() |>
  rename(rating = response) |> 
  ggplot(aes(x = herbicide, y = rating)) +
  geom_jitter(data, mapping = aes(x = herbicide, y = rating, color = brand),
              alpha = 0.05) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL), size = 2) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::number_format(scale = 10))
```




```{r}
brm(rating ~ herbicide +
                (1|run/variety), 
    data = data,
    control = list(adapt_delta = 0.95),
    family = Beta(link = "logit", 
                  link_phi = "log"),
    warmup = 1000, iter = 2000, chains = 4,
    prior = set_prior("student_t(0.5, 3, 11)", class = "b")) -> model
```





```{r}
data |> 
  pivot_wider(id_cols = c(variety, seed_treatment),
              names_from = herbicide, values_from = rating)
```

```{r}
data |> 
  group_by(seed_treatment, herbicide) |> 
  summarise(rating = mean(rating, na.rm = TRUE)) |> 
  ungroup() |> 
  ggplot(aes(x = seed_treatment, y = rating, color = herbicide, group = herbicide)) +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0,10, 2)) +

  geom_point(size = 2) +
  coord_flip() +
  geom_rect(aes(xmin = 0, xmax = 24, ymin= 0, ymax = 4), color = NA, fill = 2, alpha = 0.01) +
  geom_rect(aes(xmin = 0, xmax = 24, ymin= 4, ymax = 7), color = NA, fill = "yellow", alpha = 0.01) +
  geom_rect(aes(xmin = 0, xmax = 24, ymin= 7, ymax = 10), color = NA, fill = 3, alpha = 0.01) +
  geom_point(size = 2) +
  geom_jitter(data, 
              mapping = aes(x = seed_treatment, y = rating, color = herbicide, group = herbicide),
              alpha = 0.01, width = 1) +
  theme_bw() +
  labs(x = "seed_treatment", y = "Rating")
```

```{r}
data |> 
  group_by(herb_trait, herbicide) |> 
  summarise(rating = mean(rating, na.rm = TRUE)) |> 
  ungroup() |> 
  ggplot(aes(x = herb_trait, y = rating, color = herbicide, group = herbicide)) +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0,10, 2)) +
  geom_point(size = 2) +
  scale_color_calc() +
  geom_rect(aes(xmin = 0, xmax = 7, ymin= 0, ymax = 4), color = NA, fill = 2, alpha = 0.01) +
  geom_rect(aes(xmin = 0, xmax = 7, ymin= 4, ymax = 7), color = NA, fill = "yellow", alpha = 0.01) +
  geom_rect(aes(xmin = 0, xmax = 7, ymin= 7, ymax = 10), color = NA, fill = 3, alpha = 0.01) +
  geom_point(size = 2) +
  geom_jitter(data, 
              mapping = aes(x = herb_trait, y = rating, color = herbicide, group = herbicide),
              alpha = 0.01, width = 1) +
  theme_bw() +
  coord_flip() +
  labs(x = "Herbicide trait", y = "Rating")

ggsave("herb_trait.png")
```


```{r}
data |> 
  filter(herbicide != "ctrl") |> 
  ggplot(aes(x = herb_trait, y = rating, color = herbicide)) +
  geom_jitter()
```

